Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-02-06 ms.tex
more text and cleaning up of fringing section.

The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
We investigate whether this can manifest itself on the spectrum with the NIRCam grism.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
\textcolor{red}{double check the scatter in spectrum to photon + read noise}
\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum. Look at CV3 data, which has a tighter PSF}
}\label{fig:integratedOtisGrismSpec}
\end{figure}

The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec} and is very subtle in Figure \ref{fig:avgOtisGrismSpecFringing}, probably because of the broad PSF.
However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
\textcolor{red}{\bf Is this fringing?}

@@

>>>>

The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
Fringing will be less noticeable when many wavelengths are mixed together, but with grism spectra where the wavelengths are separated, the interference effects are more pronounced.
We investigate whether this can manifest itself on the spectrum with the NIRCam grism by looking for periodic signatures that vary in frequency as a function of wavelength.

Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing where a broadband point source is dispersed by the grism.
The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{nchdas}.
The background is subtracted with a 2nd order polynomial fit and the flux is extracted with an optimally weighted summation \citep[e.g.][]{horne1986optimalE}.
The spectrum is normalized by a 3rd order spline fit with 400 knots to remove the broad shape of the spectrum and the throughput curves.
The resulting spectrum shows high frequency ($\sim$0.2 px$^{-1}$ to $\sim$0.5 px$^{-1}$) variations far in excess of the photon and read noise.
These oscillations increase in frequency at longer wavelengths (X pixels).
The variations have peak-to-valley amplitudes of about 10\%.
However, we expect that the fringing structure will hold relatively constant during time so long as the pointing is stable at the sub-pixel level.

@@

\subsection{Extracted Spectra and periodograms}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
\textcolor{red}{In retrospect, this noise is due to the flat fielding, but averaging over many spectra with better flat fielding and some motion along the dispersion direction shows subtle fringing in Figure \ref{fig:avgOtisGrismSpecFringing}}
}\label{fig:integratedOtisGrismSpec}
\end{figure}

The fringing is very subtle in Figure \ref{fig:avgOtisGrismSpecFringing}, probably because of the broad PSF.
